An interactive environment for mapping computational structures to FPGAs

### 2016-07-07 paper/paper.tex
making progress on approach section.

  Computational structures borrowed from functional programming languages so called higher-order functions.
  These functions are very suitable to express the structure in computations and therefore a good source of parallelism~\cite{Wester15}.
  These computational structures are represented as a specific kind of dataflow graph, a cyclo static synchronous (CSDF) dataflow graph.
  Transformations are then applied to this graph to optimize performance~\cite{deGroote16}.
  During the final step, the graph is mapped to hardware by translating each node to a combinational component and replacing the edges by a FIFO.

  \begin{itemize}
    \item computational structures: \todo[inline]{elaborate a bit... big data programmers are already familiar with a structural approach to programming like hadoop}
    \item CSDF graphs and transformations
    \item simulation
    \item hardware generation using \clash \cite{Baaij10}
  \end{itemize}

@@

  In this paper we presented SDFkit, an interactive environment for designing applications using SDF graphs.
  In contrast to translating imperative programming constructs like for-loops to hardware, we use constructs to express the structure in a computation.
  Using these computational structures, the generation of highly parallel hardware is tremendously simplified.
  Applications are modeled using CSDF graphs which are a cycle-accurate model for the generated hardware.

>>>>

  Computational structures are borrowed from functional programming languages so called higher-order functions.
  These functions are very suitable to express the structure in computations and therefore a good source of parallelism~\cite{Wester15}.
  These computational structures are represented as a specific kind of dataflow graph, a cyclo static synchronous (CSDF) dataflow graph.
  Transformations are then applied to this graph to optimize performance~\cite{deGroote16}.
  During the final step, the graph is mapped to hardware by translating each node to a combinational component and replacing the edges by a FIFO.

  The main advantage of using computational structures is that there is no need to perform dependency analysis of for-loops.
  Since all dependencies are known, computations can be distributed over space and time by mathematical transformation rules.
  Even though no standard C for-loops are used to express repettive computations, this should not be a problem for programmers since similar patters are also used in map-reduce applications.
  Figure XXXXXXX shows two examples of computational structures: the higher-order function \emph{zipWith} and \emph{foldl}.
  Using \emph{zipWith} an operation is applied to pairs from two lists while \emph{foldl} reduces all elements in a list to one element.

  \missingfigure{plaatje zipw en foldl hier}

  In order to determine accuracte perfomance metric of an application, the simulation must be accurate.
  In SDFkit, the simulation can be used to for verify functional correctness as wel as performance.
  Due to a specific mapping of the application graph to hardware, a cycle accurate simulation can be performed.
  Additionally, the tokens on the edges can be changed any time allowing the user to identify bottlenecks in the graph and to tweak performance.

  \todo[inline]{hardware generation using \clash \cite{Baaij10}}
  nodes becaome combinational components and adges are implemented as FIFOs.....
  The code is generated using \clash, a fundtional hardware description language.
  each node has a peace of \clash code that represents the functionality of the node.....

@@

  In this paper we presented a methodology for designing hardware using a structured approach.
  In contrast to translating imperative programming constructs like for-loops to hardware, we use constructs to express the structure in a computation.
  Using these computational structures, the generation of highly parallel hardware is tremendously simplified.
  Applications are modeled using CSDF graphs which are a cycle-accurate model for the generated hardware.
